\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Project Statement \\  Tetris Tustle  \\{\large L02, Team \#2}}

\author{Nicholas Lobo \\ lobon3 \\ 400179304 \and
		Matthew Paulin \\ paulinm \\ 400187147 \and
		David Carrie \\ carriedd \\   000661652 \and
}

\date{January 26, 2020}



\begin{document}
\maketitle
\newpage

\tableofcontents
\newpage



\begin{table}[hp]
\section{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\hline
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\hline
1/26/2020 & Nicholas Lobo & Creating Outline\\
1/27/2020 & Nicholas Lobo & Finishing Problem Statement\\
1/27/2020 & Matthew Paulin & Finishing Problem Statement\\
1/27/2020 & David Carrie & Finishing Problem Statement\\
\hline
\end{tabularx}
\end{table}

\newpage

\section{Problem Statement}
\subsection{What is the problem to be solved?}
With the unprecedented current global situation, finding a means to alleviate loneliness and stress while also providing entertainment and enjoyment during this  pandemic is of crucial importance. Recently, the volume of large scale triple A games flooding the market have not done enough to appeal to broader demographics and cater to people wanting a more simple gaming experience. We have decided to put a spin on a simple, but beloved classic game to fill that void. Tetris took the world by storm in the 1980’s becoming the first hit game ever created by selling over 202 million copies. We are looking to take a bare bones version of this game and update it to better suit the modern standards of gaming by enhancing the graphics and adding in player versus player interaction. This will make it so that all people can pick it up and play the game easily. 

\subsection{Why is this problem important?}

Many people are currently locked indoors due to COVID-19. This disruption in daily life has cause many people to feel more depressed and isolated than ever. The need to feel entertained and connected with other people is more important now than ever and an outlet like our game can be used to combat these feelings. As the current version stands, it lacks multiplayer functionality as well as any sort of attractive UI. Updating these features and adding player versus player functionality is crucial to adding depth to the game and making it more replayable.  

\subsection{What is the problems context?}

The game is suitable for all ages and only requires a computer and an internet browser to be able to play. The game is not hardware intensive and can be played on most personal computers.  
\\
\\
The stakeholders of this project are the user players, and the developers. The software environment is a web browser and requires access to the internet for multiplayer use.


\end{document}
